### 2015-02-15 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: add meta data for PDF

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Wind Driven Residential Basement Fire - Riverdale Heights, MD},
  pdfauthor={Weinschenk, Craig G., Overholt, Kristopher J., and Madrzykowski, Daniel},
  pdfsubject={Insert abstract here.},
  pdfkeywords={insert; keywords; here}
}

>>>>

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Wind Driven Residential Basement Fire - Riverdale Heights, MD},
  pdfauthor={Weinschenk, Craig G., Overholt, Kristopher J., and Madrzykowski, Daniel},
  pdfsubject={Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on February 24, 2012, within a single-story, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two Price George's County firefighters. The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions. The fire started in the basement which generated ventilation limited (fuel rich) fire conditions in the basement area. After the front door was opened, the interior stairwell, aided by strong winds blowing into the basement, acted as a chimney for hot gases in the basement to flow towards regions of lower pressure, out through the front door. The temperature of the gases in the interior stairwell was estimated to be in excess of 400~C (750~F). Two firefighters were located in the flow path between the interior stairwell door and the front door of the structure, were exposed to these elevated temperatures, and suffered serious burn injures. Five additional firefighters were injured during fire operations on the first floor.},
  pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
}
